Jane, John … Leslie? A Historical Method for Algorithmic Gender Detection

### 2014-09-19 article.Rmd
Note on SSA data

**I moved this next caveat section about the SSA data because it felt kind of out of place sandwiched between the two examples. I'm still not sure it fits here, though. I'm trying to figrue out if there's a way to integrate it into the paper that isn't going to be quite so diversionary for the reader.**

>>>>

**I moved this next caveat section about the SSA data because it felt kind of out of place sandwiched between the two examples. I'm still not sure it fits here, though. I'm trying to figrue out if there's a way to integrate it into the paper that isn't going to be quite so diversionary for the reader. LAM: okay, wherever you think is best.**
